The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-31 final/paper/main.tex
update paper

\section*{Abstract}
Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
applications with noise (DBSCAN).

@@

In this work, the dataset on Synapse.org is used, which contains 20531 RNA sequences and 3 types of cancer 
in the train data, i.e., kidney renal clear cell carcinoma (KIRC), breast invasive carcinoma (BRCA), 
lung adenocarcinoma (LUAD), and 2 new types in test data, i.e., colon adenocarcinoma (COAD), 
prostate adenocarcinoma (PRAD). And also, the dataset of arrhythmia is included, which caintains
8 types in train data, and 5 new types in test data. To find out which techniques is more suitable to fit 
these two datasets, this work examines the the accuracy of the combinations of some major machine 
learning techniques, including PCA, AE, KNN, SVM, NN, k-means, DBSCAN.

>>>>

\section*{Abstract}
Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), support vector data 
description (SVDD), neural network (NN) and naive Bayes classifier; and clustering for dealing with unknown 
types, e.g., k-means, density-based spatial clustering of applications with noise (DBSCAN).

@@

In this work, the dataset on Synapse.org is used, which contains 20531 RNA sequences and 3 types of cancer 
in the train data, i.e., kidney renal clear cell carcinoma (KIRC), breast invasive carcinoma (BRCA), 
lung adenocarcinoma (LUAD), and 2 new types in test data, i.e., colon adenocarcinoma (COAD), 
prostate adenocarcinoma (PRAD). And also, the dataset of arrhythmia is included, which caintains
8 types in train data, and 5 new types in test data. To find out which techniques is more suitable to fit 
these two datasets, this work examines the the accuracy of the combinations of some major machine 
learning techniques, including PCA, AE, KNN, SVM, SVDD, NN, naive Bayes classifier, NN-chain, k-means, 
DBSCAN.
